---
title: "Nigeria:A summary of State creation from 1967-Till date"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```



#Summary
<h2>Summary</h2>
Nigeria has created thirty six federal states since her independance in October 1960. Below is a table showing the names of federal states and their date of creation since 1967.

| State             	| Date Created      	|
|-------------------	|-------------------	|
| Abia State        	| 27 August 1991    	|
| Adamawa State     	| 27 August 1991    	|
| Akwa Ibom State   	| 23 September 1987 	|
| Anambra State     	| 27 August 1991    	|
| Bauchi State      	| 3 February 1976   	|
| Bayelsa State     	| 1 October 1996    	|
| Benue State       	| 3 February 1976   	|
| Borno State       	| 3 February 1976   	|
| Cross River State 	| 27 May 1967       	|
| Delta State       	| 27 August 1991    	|
| Ebonyi State      	| 1 October 1996    	|
| Edo State         	| 27 August 1991    	|
| Ekiti State       	| 1 October 1996    	|
| Enugu State       	| 27 August 1991    	|
| Gombe State       	| 1 October 1996    	|
| Imo State         	| 3 February 1976   	|
| Jigawa State      	| 27 August 1991    	|
| Kaduna State      	| 27 May 1967       	|
| Kano State        	| 27 May 1967       	|
| Katsina State     	| 23 September 1987 	|
| Kebbi State       	| 27 August 1991    	|
| Kogi State        	| 27 August 1991    	|
| Kwara State       	| 27 May 1967       	|
| Lagos State       	| 27 May 1967       	|
| Nasarawa State    	| 1 October 1996    	|
| Niger State       	| 3 February 1976   	|
| Ogun State        	| 3 February 1976   	|
| Ondo State        	| 3 February 1976   	|
| Osun State        	| 27 August 1991    	|
| Oyo State         	| 3 February 1976   	|
| Plateau State     	| 3 February 1976   	|
| Rivers State      	| 3 February 1976   	|
| Sokoto State      	| 3 February 1976   	|
| Taraba State      	| 27 August 1991    	|
| Yobe State        	| 27 August 1991    	|
| Zamfara State     	| 1 October 1996    	|


#Register

Column {data-width=550}
-----------------------------------------------------------------------

###About us
<a href="https://mapsnigeriainitiative.com">&copy;mapsnigeriainitiative</a> is a non-profit initiative established with the aim of sharing technical information and experience in the area of geospatial data gathering, processing, storage, interpretation and dissemination with the general public.<br><br>
<a href="https://mapsnigeriainitiative.com/register">Register</a> and get free access to GIS tutorials and webinars on various topics in Desktop GIS, Web GIS, Web Cartography and Web mapping applications.
<br><br><br>

<strong>Contact</strong>
Email: admin@mapsnigeriainitiative.com
Live Chat: 3-5pm Saturdays (mapsnigeriainitiative.com)<br><br>

&copy;<small></em>Contents of this work are the intellectual property of mapsnigeriainitiative. All rights reserved.Contributions from wikipedia, openstreetmap, carto</em></small><br>

##Upcoming activities

```{r fig.width = 6, fig.height = 6, echo=FALSE}
library(jpeg)
library(grid)
img <- readJPEG("C:/Users/user/Desktop/out.jpg")
 grid.raster(img)
```


#1967-1976

Column {data-width=550}
-----------------------------------------------------------------------

###<strong>Administrative Map of Nigeria as at 1976 with 19 states</strong>
<small>Mouse Click on the feature boundaries to display info</small>
```{r echo=FALSE}
library(leaflet)
library(raster)
first <- shapefile("C:/New folder/1976.shp")
leaflet(width='80%')%>%
  addTiles()%>%
  setView(lng=7.30, lat=9.00, zoom=6)%>%
  addPolygons(data = first,weight = 1, fill = TRUE, stroke = TRUE, color = "#000",  popup = paste0(paste0("<strong style='color:red'>Name: </strong>", 
                      first$name, 
                      "<br><strong>Createdate: </strong>", 
                      first$createdate)
  ), group = "first")

```



#1976 - till date

Column {data-width=550}
-----------------------------------------------------------------------

###<strong>Administrative Map of Nigeria as of today with 36 federal states<br>
<small>Mouse Click on the feature boundaries to display info</small>
```{r}
library(leaflet)
library(raster)
second <- shapefile("C:/New Folder/adm.shp")
leaflet(width='80%')%>%
  addProviderTiles("CartoDB.Positron")%>%
  setView(lng=7.30, lat=9.00, zoom=6)%>%
 addPolygons(data = second,weight = 1, fill = TRUE, stroke = TRUE, color = "red",  fillOpacity = 0.2, popup = paste0(paste0("<strong style='color:red'>Name: </strong>", 
                      second$NAME_1, 
                      "<br><strong>Createdate: </strong>", 
                      second$createdate)
  ), group = "second")
```


