---
title: "Drawing features on web maps using Leaflet and R"
author: "mapsnigeriainitiative.com"
date: "September 26, 2016"
output: html_document
code_folding: hide
---

This tutorial will demonstrate the use of leaflet and raster packages in R to draw features as layers onto a web map.The demo will use different types of datasets in shapefile and geojson formats.

Install the library(raster) package from the Packages tab.
Install the library(jsonlite) package too.

Download zipped folder with your sample data for practice by clicking here:https://www.dropbox.com/s/dmi8rae97pzr7bq/shapefiles.zip?dl=0


Write the R argument below into the console and press Enter after the last line. Click the viewer tab to see result. 


```{r}
library(leaflet) 
library(raster)
dd<-shapefile("C:/shapefiles/occurclay.shp") # use this code to add your shapefile from your local directory
cc<-shapefile("C:/states shapefiles/delta.shp")
leaflet(width = "100%")%>% addTiles(attribution = "overlay data© mapsnigeriainitiative 2016")%>% setView(6, 6, 8) %>%  # add the default basemap along with setting the view (lng, lat) and initial zoom 
   addPolygons(data = cc, fill=TRUE, stroke = TRUE, color = "red", popup = paste0("Name:",cc$NAME_2,"<br>", "Pop:", cc$total))%>% #add the polygon features along with CSS style and popup display
addCircleMarkers(data = dd, fill = TRUE, stroke = TRUE, color = "#000", fillColor = "blue", radius = 8, weight = 1) #add the points as circular markers and add CSS style. Press the Enter key
```


Make sure you write the correct directory to your shapefile. 

Next we add a dataset that is in geojson format. Write the R argument below onto the console and press Enter after the last line. Click the viewer tab to see result.


```{r}
library(jsonlite)
library(leaflet)
spots <- readLines("https://cdn.rawgit.com/mayotunde/cluster/gh-pages/spot.geojson")%>%  paste(collapse = "\n") #use the <-readlines to load a geojson file from an external url into the rstudio
leaflet(width = "100%") %>% #initialize the leaflet map
setView(lng = 4.6, lat = 2.8, zoom = 3)%>% #set the view and initialize zoom of the map
  addTiles(attribution = "overlay data© mapsnigeriainitiative 2016")%>% #add the base maps from CartoDB 
 addGeoJSON(spots) # Draw the geojson file onto the map and Press the enter key
```


* There is no provision for adding CSS styles to geojson point features for now.

Now that is done, you can go ahead and use the Publish icon to share your leaflet map on the web.
